---
title: "INFO 550 Report"
author: "Alessia Kettlitz, Evelyn Shi, Xinyi Dan, and Yijing (Monica) Zhu"
date: "`r Sys.Date()`"
output: html_document
---

```{r, read-config, include = FALSE}
which_report <- Sys.getenv("REPORT_TYPE")
param_list <- config::get(
  config = which_report
)
```

```{r, set-chunk-opts, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r, load-data}
data <- read.csv(
  here::here("course_engagement.csv"), header = TRUE
)
```

## Summary Statistics
Some summary statistics for our engagement data:

```{r, summary-stats, eval = param_list$summary}
# read in Monica's summary statistics data
summary_stats <- read.csv(
  here::here("output/Monica/summary_statistics_by_topic.csv"), header = TRUE
)

# cleaning/editing the data
summary_stats <- subset(summary_stats, select = -c(X))
summary_stats[,c("video_length","unique_viewers")] <- round(summary_stats[,c("video_length","unique_viewers")], digits = 2)
summary_stats <- summary_stats[order(summary_stats[,"unique_viewers"], decreasing = TRUE),]
colnames(summary_stats) <- c("Video Topic", "Video Length", "No. of Unique Viewers")

# creating table
summary_stats_table <- knitr::kable(
   summary_stats
)
summary_stats_table
```

## Most Popular Videos and Topic Demographics

These are the 5 most popular videos by views:
```{r, top-5-popular, eval = param_list$demographics}
# read in the Xinyi's data
top5popular <- read.csv(
  here::here("output/Xinyi/top5_popular.csv"), header = TRUE
)

# cleaning the data
top5popular <- subset(top5popular, select = -c(X, reupload))
top5popular[,"video_length"] <- round(top5popular[,"video_length"], digits = 2)
top5popular <- top5popular[order(top5popular[,"views"], decreasing = TRUE),]
colnames(top5popular) <- c("Week", "Video Number", "Video Title", "Topic", "Views", "Unique Viewers", "Video Length", "Video Length")

# creating a table
top5_table <- knitr::kable(
   top5popular
)
top5_table
```

These are the 5 least popular videos:
```{r, bot-5-popular, eval = param_list$demographics}
# reading in Xinyi's data
bot5popular <- read.csv(
  here::here("output/Xinyi/bot5_popular.csv"), header = TRUE
)

# cleaning
bot5popular <- subset(bot5popular, select = -c(X, reupload))
bot5popular[,"video_length"] <- round(bot5popular[,"video_length"], digits = 2)
bot5popular <- bot5popular[order(bot5popular[,"views"]),]
colnames(bot5popular) <- c("Week", "Video Number", "Video Title", "Topic", "Views", "Unique Viewers", "Video Length", "Video Length")

# making a table
bot5_table <- knitr::kable(
   bot5popular
)
bot5_table
```

The following is a table of video topic demographics.
```{r, topic-demographics, eval = param_list$demographics}
# reading in the output data for topic demographics
demo <- read.csv(
  here::here("output/Xinyi/demographics.csv"), header = TRUE
)

# formatting the data
demo <- subset(demo, select = -c(X))
colnames(demo)[1] <- "Topic:"

#making and printing a table
demo_table <- knitr::kable(
   demo
)
demo_table
```

## Correlation

Here, we look at the correlation between length of video and number of views, shown below in this scatterplot.
```{r, correlation-scatterplot, eval = param_list$correlation}
knitr::include_graphics(
  here::here("output/Alessia/correlation_scatterplot.png")
)
```